### 2023-07-31 2.State/lstm.tex
Chnages, might not work anymore since latexmk...

\subsubsection{\acf{FGR} \ac{LSTM}}
This variant of the \ac{LSTM} is the most complex of all. This is due to the amount of feedback connections. This is basically a more complex version of the Vanilla \ac{LSTM}. The modified equations are :
\begin{equation}\label{eq:inputGVanilla}
  i_t=\sigma (w_i\cdot[x_{t_1},h_{t-1}]+ R_{ii}\cdot i_{t-1} + R_{if}\cdot f_{t-1} + R{io}\cdot o_{t-1} + b_i+c_{t-1}\odot p_f)
\end{equation}
\begin{equation}\label{eq:forgetGVanilla}
  f_t=\sigma (w_f\cdot[x_{t_1},h_{t-1}]+ R_{fi}\cdot i_{t-1} + R_{ff}\cdot f_{t-1} + R{fo}\cdot o_{t-1} + b_f+c_{t-1}\odot p_i)
\end{equation}
\begin{equation}\label{eq:ouputGVanilla}
  o_t=\sigma (w_o\cdot[x_{t_1},h_{t-1}]+ R_{oi}\cdot i_{t-1} + R_{of}\cdot f_{t-1} + R{oo}\cdot o_{t-1} + b_o+c_{t}\odot p_o)
\end{equation}
With $R_{fi}$ being the weight matrix of the input feedback connection to compute the forget gate, and the same goes for the other weight matrices.

>>>>

\subsubsection{\acf{FGR} \ac{LSTM}}
This variant of the \ac{LSTM} is the most complex of all. This is due to the amount of feedback connections. This is basically a more complex version of the Vanilla \ac{LSTM}. The modified equations are :
\begin{equation}\label{eq:inputGFGR}
  i_t=\sigma (w_i\cdot[x_{t_1},h_{t-1}]+ R_{ii}\cdot i_{t-1} + R_{if}\cdot f_{t-1} + R{io}\cdot o_{t-1} + b_i+c_{t-1}\odot p_f)
\end{equation}
\begin{equation}\label{eq:forgetGFGR}
  f_t=\sigma (w_f\cdot[x_{t_1},h_{t-1}]+ R_{fi}\cdot i_{t-1} + R_{ff}\cdot f_{t-1} + R{fo}\cdot o_{t-1} + b_f+c_{t-1}\odot p_i)
\end{equation}
\begin{equation}\label{eq:ouputGFGR}
  o_t=\sigma (w_o\cdot[x_{t_1},h_{t-1}]+ R_{oi}\cdot i_{t-1} + R_{of}\cdot f_{t-1} + R{oo}\cdot o_{t-1} + b_o+c_{t-1}\odot p_o)
\end{equation}
With $R_{fi}$ being the weight matrix of the input feedback connection to compute the forget gate, and the same goes for the other weight matrices.
